---
title: "Video Games Dashboard"
resource_files:
- Video_Game_Sales_as_of_Jan_2017.csv
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    source_code: embed
    theme: simplex
---
```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(plotly)
library(shiny)
library(shinydashboard)
library(rgl)
library(plot3D)
```
```{r global, include=FALSE}
data <- read.csv("D:/CLASS FOLDER/SEM 4/DataViz/Finalproject/datavizdata.csv",
                 stringsAsFactors=FALSE)
```
Data View
===
Column {.sidebar}
---
```{r}
selectInput("GENREVIEW", h3("Genre Filter :"), 
            choices = c(as.character(unique(data$Genre))),
            selected = "Action")
selectInput("PLATFORMVIEW", h3("Platform Filter :"), 
            choices = c(as.character(unique(data$Platform))),
            selected = "NES")
```
Introduction.
This dataset contains a list of video games with sales greater than 100,000 copies. It was generated by a scrape of vgchartz.com.
Dashboard by Amri Rohman.
Sidoarjo, 1 September 2019.
Row
---

```{r}
#valueBox(dim(data)[1], icon = "fa-comments")
```
```{r}
#valueBox(dim(data)[2], icon = "fa-comments")
```
```{r}
#valueBox(unique(data$Genre)%>%length(), icon = "fa-user")
```
```{r}
#valueBox(unique(data$Platform)%>%length(), icon = "fa-user")
```
Row
---
### Data View
```{r}
renderTable({
  data[,c(1:10)] %>%
    filter(Genre==input$GENREVIEW) %>% 
    filter(Platform==input$PLATFORMVIEW) %>%
    head(20)
  })
```

Chart
===
Column {.sidebar}
---
```{r}
selectInput("GENRE", h3("Genre Filter :"), 
            choices = c(as.character(unique(data$Genre))),
            selected = "Action")
```

Column
---
### Total Global Sales Line Plot by Genre

```{r}
renderPlotly({
data %>%
  group_by(Year, Genre) %>%
  summarise(Total_Global_Sales = sum(Global_Sales),.groups = 'keep') %>%
  filter(Genre==input$GENRE) %>%
  data.frame() %>% 
  plot_ly(x = ~Year, 
          y = ~Total_Global_Sales,
          type = "scatter",
          mode = "lines+markers")
})
```

### Count Video Games Genre
```{r}
data %>%
  group_by(Genre) %>%
  summarise(Count = n()) %>%
  plot_ly(x = ~Genre,
          y = ~Count,
          type = "bar")
```
Scatter plot
===
Column {.sidebar}
---
```{r}
selectInput("XA", h3("Select X axis :"), 
            choices = c("NA_Sales", "EU_Sales", "JP_Sales", "Other_Sales", "Global_Sales"),
            selected = "NA_Sales")
selectInput("YA", h3("Select Y axis :"),
            choices = c("NA_Sales", "EU_Sales", "JP_Sales", "Other_Sales", "Global_Sales"),
            selected = "NA_Sales")
```
Row
---
### Scatter plot
```{r}
renderPlotly({
  data %>%
  plot_ly(x = data[,c(input$XA)],
          y = data[,c(input$YA)])
  })
```


### Correlation Plot
```{r}
data[, c("NA_Sales", "EU_Sales", "JP_Sales", "Other_Sales", "Global_Sales")] %>%
  cor(method = "pearson") %>%
  corrplot::corrplot(addCoef.col = "white")
```

----

3D-Plots
===
Row
---

```{r}
fig <- plot_ly(data, x = ~Critic_Score, y = ~User_Score, z = ~User_Count, type = 'scatter3d', mode = 'lines+markers', line = list(width = 3, color = ~Year, colorscale = 'Viridis'),
               marker = list(size = 3.5, color = ~Year,  colorscale = 'Greens', cmin = -20, cmax = 50))
fig
```

---
```{r}
colors <- c('#4AC6B7', '#1972A4', '#965F8A', '#FF7070', '#C61951','Red')

fig <- plot_ly(data, x = ~Global_Sales, y = ~Other_Sales, z = ~User_Count, color = ~Platform, size = ~User_Count, colors = colors,
               marker = list(symbol = 'circle', sizemode = 'diameter'), sizes = c(5, 150),
               text = ~paste('Name:', Name, '<br>Other_Sales:', Other_Sales, '<br>Global_Sales:', Global_Sales,
                             '<br>User_Count', User_Count))
fig <- fig %>% layout(title = '..',
                      scene = list(xaxis = list(title = 'Global_Sales',
                                                gridcolor = 'rgb(255, 255, 255)',
                                                #range=c(1,2),
                                               
                                                type = 'log',
                                                zerolinewidth = 1,
                                                ticklen = 5,
                                                gridwidth = 2),
                                   yaxis = list(title = 'Other_Sales',
                                                gridcolor = 'rgb(255, 255, 255)',
                                                #range=c(1,5),
                                                
                                                zerolinewidth = 1,
                                                ticklen = 5,
                                                gridwith = 2),
                                   zaxis = list(title = 'User_Count',
                                                gridcolor = 'rgb(255, 255, 255)',
                                                #range=c(1000,10000),
                                                type = 'log',
                                                zerolinewidth = 1,
                                                ticklen = 5,
                                                gridwith = 2)),
                      paper_bgcolor = 'rgb(243, 243, 243)',
                      plot_bgcolor = 'rgb(243, 243, 243)')

fig
```